---
title: "5/3/1 Two-day program"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(magrittr)
library(dplyr)
library(tidyr)
library(ggplot2)
```


## Setting Training Max

Find your training 1RM (pg.21):

$$
weight * reps * 0.0333 + weight = \texttt{1RM}
$$
Then 

$$
\texttt{1RM} * 0.9 = \texttt{1RM Training Max}
$$

### Training maxes

If incrementing from a previous round, add 10 to squat / deadlift, 5 to bench or overhead

**Training maxes:**

```{r}
lifts <- data.frame(lift =        c("fsquat", "bench", "dead", "press"),
                    training_max = c(205,     220,     385,    170))
```

## Calculating lifts

Percentages

```{r}
week_perc <- tibble::tribble(
  ~week,    ~type, ~perc, ~reps,
     1L, "warmup",   0.4,    5L,
     1L, "warmup",   0.5,    5L,
     1L, "warmup",   0.6,    3L,
     1L,   "main",  0.65,    5L,
     1L,   "main",  0.75,    5L,
     1L,   "main",  0.85,    5L,
     2L, "warmup",   0.4,    5L,
     2L, "warmup",   0.5,    5L,
     2L, "warmup",   0.6,    3L,
     2L,   "main",   0.7,    3L,
     2L,   "main",   0.8,    3L,
     2L,   "main",   0.9,    3L,
     3L, "warmup",   0.4,    5L,
     3L, "warmup",   0.5,    5L,
     3L, "warmup",   0.6,    3L,
     3L,   "main",  0.75,    5L,
     3L,   "main",  0.85,    3L,
     3L,   "main",  0.95,    1L
  )


```

Making a list for the progression of each of the lifts:

```{r}
prog.ls <- apply(X = lifts, 1, function(x){
  tmp <- week_perc
  weights <- (week_perc$perc * as.integer(x[2]))
  tmp$lift <- x[1]
  tmp$weight <- round(weights / 5) * 5
  return(tmp)
})

names(prog.ls) <- lifts$lift
```


## completed lifts

code to create the tribble to input my reps, run interactively:

```{r eval=FALSE}
lapply(prog.ls, function(x){
  x %>% filter(type == "main") %>%
    group_by(week) %>% 
    slice(3) %>% 
    ungroup %>% 
    select(week, lift, weight)
}) %>% bind_rows %>% 
  arrange(week) %>% 
  mutate(reps = NA) %>% 
  datapasta::dpasta()
```

handcrafted data entry: 

```{r}
accomplished <- tibble::tribble(
  ~week,    ~lift, ~weight, ~reps,
     1L, "fsquat",     175,    5,
     1L,  "bench",     185,    8,
     1L,   "dead",     325,    6,
     1L,  "press",     145,    5,
     2L, "fsquat",     185,    5,
     2L,  "bench",     200,    5,
     2L,   "dead",     345,    5,
     2L,  "press",     155,    4,
     3L, "fsquat",     195,    4,
     3L,  "bench",     210,    4,
     3L,   "dead",     365,    5,
     3L,  "press",     160,    2
  ) %>% 
  mutate(calc1RM = weight*reps*0.0333 + weight) %>% 
  filter(complete.cases(.))

```


Let's make a plot!

```{r}
library(ggplot2)

accomplished %>% 
  ggplot(aes(x = as.factor(week), y = calc1RM)) + 
  geom_line(aes(group = lift, color = lift), size = 2) +
  labs(x = "Week",
       y = "Calculated 1RM")
```


## Saving data

Adding in a date column to match with week. 

```{r}
dates <- tibble::tribble(
  ~week, ~date,
   1,     "2019-03-18",
   2,     "2019-03-25",
   3,     "2019-04-01"
) %>%
  mutate(date = ymd(date))
```


```{r}
lift_tbl <- left_join(accomplished, dates) %>% 
  select(week, date, lift:calc1RM)
```

```{r}
write.csv(x = lift_tbl, file = "data/2019-03_lift-data.csv",
          quote = FALSE, row.names = FALSE)
```


